Lynott et al. (2014) - Potential error in statistics reporting

### 2017-11-15 manuscript.Rmd
Corrected an earlier error where I had mistaken the reference Norman et al., 2003, for Norman et al., 2004. Changed it back to the (correct) 2003 reference, both in Zotero and in all citations in the manuscript.

Another example of an objectively determined SESOI can be found in @Button2015 where the minimal clinically important difference on the Beck Depression Inventory - II was determined by asking 1039 patients when they subjectively felt less depressed (i.e., when they personally noticed an improvement) and relating this to the corresponding difference score on the depression inventory.

@Norman2004 used a wide range of methods to determine the minimally important (or detectable) difference in measures for the quality of life in chronic diseases, and observe a surprisingly consistent minimally important difference of half a standard deviation, or $d = 0.5$. They make the argument that this bound of approximately half a standard deviation could be related to the limits of human discriminability. Therefore, even though a SESOI of $d = 0.5$ might seem quite large, it could be a plausible equivalence bound when examining effects that should be noticeable by single individuals.

@@

As with any statistical test, the usefulness of the result of an equivalence test depends on the question we ask. The question manifests itself in the bounds we set: Is our data surprising if the true effect lies outside of the bounds? If we test against very wide bounds, observing statistical significance can hardly be considered surprising, given that most effects in psychology are small to medium [@Hemphill2003]. Examining the papers citing @Lakens2017a, we see some researchers state a SESOI without providing a justification for it [@Brown2017; @Schumann2017].^[In these two cases, one could perhaps guess that benchmark values for a Cohen’s d of “medium” size was chosen.] An equivalence test using a SESOI of $d = 0.5$ might very well answer a question the researchers are interested in [for one possible justification based on minimally important differences, see @Norman2004], but researchers should always provide a detailed justification of their chosen SESOI, given that this is in essence a justification for why they ask a specific question from their data.

>>>>

Another example of an objectively determined SESOI can be found in @Button2015 where the minimal clinically important difference on the Beck Depression Inventory -- II was determined by asking 1039 patients when they subjectively felt less depressed (i.e., when they personally noticed an improvement) and relating this to the corresponding difference score on the depression inventory.

@Norman2003 used a wide range of methods to determine the minimally important (or detectable) difference in measures for the quality of life in chronic diseases, and observe a surprisingly consistent minimally important difference of half a standard deviation, or $d = 0.5$. They make the argument that this bound of approximately half a standard deviation could be related to the limits of human discriminability. Therefore, even though a SESOI of $d = 0.5$ might seem quite large, it could be a plausible equivalence bound when examining effects that should be noticeable by single individuals.

@@

As with any statistical test, the usefulness of the result of an equivalence test depends on the question we ask. The question manifests itself in the bounds we set: Is our data surprising if the true effect lies outside of the bounds? If we test against very wide bounds, observing statistical significance can hardly be considered surprising, given that most effects in psychology are small to medium [@Hemphill2003]. Examining the papers citing @Lakens2017a, we see some researchers state a SESOI without providing a justification for it [@Brown2017; @Schumann2017].^[In these two cases, one could perhaps guess that benchmark values for a Cohen’s d of “medium” size was chosen.] An equivalence test using a SESOI of $d = 0.5$ might very well answer a question the researchers are interested in [for one possible justification based on minimally important differences, see @Norman2003], but researchers should always provide a detailed justification of their chosen SESOI, given that this is in essence a justification for why they ask a specific question from their data.
